---
title: 'R vs Python: install.package vs import'
author: "Chi Xin"
date: "February 16, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### _**We believe two languages can be killed with one stone! **_

*** 
***

Since both R and Python are open source programming language, learning how to import packages becomes important for beginners. Today, I will show how to install data.table package in R and import numpy package into python. Noted that both data.table and numpy are very useful packages when manipulating and cleaning data in R and Python. 

In R: 

```{r}
# download and install your package from CRAN 
install.packages("dplyr", repos="http://cran.rstudio.com/")

# recall it in your library 
library(dplyr) # no quote needed


```

*** 

In Python, you have to import the package; os, first  
```{python }
import numpy as np
# you can give numpy a nickname such as "np" here just for quick reference

# check if it is imported
import sys
print("Check if numpy has been imported:", 'numpy' in sys.modules)

```


```



