---
title: "R vs Python Map Filter Reduce"
author: Lawrence Liu
date: March 26, 2017
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### _**We believe two languages can be killed with one stone! **_

*** 
***

There are some common higher-order functions in functional programming languages. In R they are `Reduce`, `Filter`, `Map`. We compare them with their Python counterparts.


####In R
```{r}
nums <- 1:10
#apply sum to nums and reduce it to a single number
Reduce(sum, nums)
#choose even number from nums
Filter(function(x) x %% 2 == 0, nums)
#multiple every element in nums with 2
as.numeric(Map(function(x) x * 2, nums))
```

####In Python
```{python, engine.path="/Users/lawrence/anaconda/bin/python"}
nums = xrange(1,11)
#apply sum to nums and reduce it to a single number
print reduce(lambda x, y: x + y , nums), '\n'
#choose even number from nums
print filter(lambda x: x % 2 == 0, nums), '\n'
#multiple every element in nums with 2
print map(lambda x: x * 2, nums), '\n'
```


###Usage of higer-order functions.
e.g. `*` is a binary operator, but `prod` in R can be applied to a vector. Reduce can be used to implement a prod function which takes a numeric vector with any length.
```{r}
x <- 1:10
#prod1 can only take 2 numbers
prod1 <- function(a, b)
  return(a * b)

#prod2 can take a numeric vector
prod2 <- function(vec){
  Reduce(prod1, vec)
}

prod2(x)
```

