---
title: 'R vs Python: fread vs pd.read_csv'
author: "Chi Xin"
date: "March 22, 2017"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
### _**We believe two languages can be killed with one stone! **_

*** 
***

Following the last part, today we will see how to read a txt file into R and Python. 

***
In R: There are multiple ways to read a txt file into R. Here, we recommend using the data.table package instead of read.table. There are a lot benefits of using data.table; here we will leave more details of data.table packages to the future.    


```{r, warning=FALSE}

# install.packages("data.table")
library(data.table)

iris = fread(input = 'iris.txt',
             na.strings="NA", # A character vector of strings which are to be interpreted as NA values
             stringsAsFactors=FALSE, # Convert all character columns to factors? 
             nrows=-1L, # The number of rows to read, by default -1 means all
             colClasses=c("integer", "numeric", "numeric", "numeric", "numeric", "factor") 
             # A character vector of classes (named or unnamed)
             )


# assign column names 
setnames(iris, c("id", "sepal_length ", "sepal_width", "petal_length", "petal_width", "class"))

# check your data
head(iris, 5)



```

*** 

In Python:
```{python, warning=FALSE}
# here, we still use pd.read_csv from the pandas package.
import pandas as pd
iris = pd.read_csv('iris.txt', sep="\t") # note here, we use "\t" as the sepreate symbol since it is a txt file. 

print(iris.head(5))

```

